### 2024-08-11 doc/Thesis/chapter/01-introduction.tex
nearly finish with todos from todo.md

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is a viable renewable energy source towards energy neutrality.
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g.\ wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
%
One type  of thin film PV is based on the CIGS (copper indium gallium sulfide) semiconductor absorber\cite{Vasekar2010}. 
Due to the large light absorption coefficient of CIGS (compared to silicon), less absorber material is needed (a couple of micrometers) and the PV cell can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple solar cells are connected in series. 
The solar cells must be deposited on a non-conducting surface.
Glass is a popular non-conducting substrate, but rigid and brittle. 
A flexible alternative is steel foil, which is ductile, inexpensive and highly available, but electrically conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
Polymers would be a choice if not for their low thermal stability which does not permit high production temperatures.
A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g.\ tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
Sol-gel processes often produce porous layers, though.

In this work a dense, insulating and homogeneous layer of \ch{ZrO2} is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the deposited layer on the coating parameters.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the electrical conductance of the layer is performed with a particle swarm optimization 
algorithm which has the coating process variables as input. 
%The resulting optimum is compared with other optimization methods.
%\td{and how do you transfer knowledge ...}

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is a viable renewable energy source towards energy neutrality.
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g.\ wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission}, which harness the whole power output of the sun.
%
One type  of thin film PV is based on the CIGS (copper indium gallium sulfide) semiconductor absorber\cite{Vasekar2010}. 
Due to the large light absorption coefficient of CIGS (compared to silicon), less absorber material is needed (a couple of micrometers) and the PV cell can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple solar cells are connected in series. 
The solar cells must be deposited on a non-conducting surface.
Glass is a popular non-conducting substrate, but rigid and brittle. 
A flexible alternative is steel foil, which is ductile, inexpensive and highly available, but electrically conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
Polymers would be a choice if not for their low thermal stability, which does not permit high production temperatures.
A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g.\ tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
Sol-gel processes often produce porous layers, though.

In this work a dense, insulating and homogeneous layer of \ch{ZrO2} is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the deposited layer on the coating parameters.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the electrical conductance of the coating layer is performed with a particle swarm optimization 
algorithm which has the coating process variables as input. 
%The resulting optimum is compared with other optimization methods.
%\td{and how do you transfer knowledge ...}

### 2024-08-11 doc/Thesis/chapter/020-theory-materials.tex
nearly finish with todos from todo.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into electric energy can be broken down into two essential steps: 
the generation of an electron-hole pair through photon absorption, the electron-hole separation by the built in electric field at the p-n junction and finally collection of the electrons and holes at the opposite terminals of the device\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
%This is often achieved through a p-n junction.
The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g.\ silicon); if not, heterojunctions (e.g.\ \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

@@

The band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium-gallium and sulfur-selenium ratios.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in the 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources\cite{hedstrom1993cigs}.
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} n-type layer (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
After the \ch{CdS} layer 
A window layer of intrinsic \ch{ZnO} is deposited after the \ch{CdS}, followed by a highly conductive aluminium doped layer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the aluminium doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and polymers (e.g.\ polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Polymers generally have low thermal stability compared with ceramics and metals which restrict the fabrication temperature of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
Thus, an insulating layer has to be deposited on the steel substrate. 
%The conductance of steel can be masked by a insulator layer (e.g.\ \ch{ZrO2}, \ch{Al2O3}).

@@

%\section{Materials and Their Analysis}
\section{Sample preparation}
%\todo{COATING OF THE SUBSTRATE or sample preparation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties of Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}). 
This prevents mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
\ch{ZrO2} is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and bases\cite{Nielsen2005}.
%Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contact Deposition by Sputtering}
%SPUTTERING FREEWRITING: 
% what is sputtering?
Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
% what can it be used for? 
%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
%
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputter-deposited thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.
% how does it work? 
%A plasma is created and the ions are accelerated to the surface. 
The ions, which are accelerated to the surface, mostly originate from a plasma.
The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
The cascade can reach the surface again. 
If the energy of an atom is larger than the binding energy, the atom is ejected. 
%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
a minimum pressure is needed to sustain the plasma.
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
% what is used? 
Nobel gases (e.g.\ argon) in plasma phase are mainly used for bombardment because of their inert properties. 
Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
%Reactive gases can be added (e.g.\ \ch{O2} or \ch{N2}).
In order to use sputtering for depositing a target material on top of a substrate material, 
the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).

@@

\iffalse
%\td{how does it work?}\\
A high voltage is applied to 
two parallel electrodes with low pressure gas in between. 
The target acts as as feedstock anode and the substrate (holder) as cathode (see figure \ref{fig:sputter0}).
%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
The anode, then, emits electrons which collide with gas particles (mostly argon because of its inert nature and potential to transfer more kinetic than lighter noble gases). 
Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
If a cation has enough energy, it will bump off one or more atoms or molecules from the surface. 
This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter1}). 
\fi

@@

\subsubsection{Infrared spectroscopy}
% IR
\Gls{ir} light interacts with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore be calculated to be
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active, except Raman spectroscopy. 
%\td(does Raman not also use IR)}
The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns in the so called fingerprint region. 
These transition are mostly "forbidden" and allow analysis of bulk matter without extensive preparation
due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.
\fi
%\td{describe simple IR with monochromator}

@@

\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident angle) were recorded with a Bruker Vertex 70 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588} {\nano\meter}) and a silicon detector for visual and \gls{nir} light (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). 
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
For transmittance the light entered the sample from the side with the layer. 
The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
%
%When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline structure of materials.
Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids, 
the beams get reflected and contain information about the structure\cite{Kaliva2020}.
Each crystalline material has a discreet atomic structure, which upon irradiation with 
X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into electric energy can be broken down into two essential steps: 
the generation of an electron-hole pair through photon absorption, the electron-hole separation by the built in electric field at the p-n junction and finally collection of the electrons and holes at the opposite terminals of the device\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
%This is often achieved through a p-n junction.
The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g.\ silicon); if not, heterojunctions (e.g.\ \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules, which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

@@

The band gap of CIGS can be varied between \ev{1} and \ev{1.7} by varying the indium-gallium and sulfur-selenium ratios.
This is a result of the large difference of band gaps of \ch{CuInSe2} and \ch{CuGaSe2} (see table \ref{tab:cigs}). 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In figure \ref{fig:cigs} the schematic layer sequence of a standard \gls{cigs} thin film cell is shown. 
Typically, a \um{1} thick molybdenum layer is deposited on soda lime glass. 
The sodium in the glass diffuses through the molybdenum layer and increases efficiency and reliability by directing the growth of \gls{cigs} in the 112 direction\cite{hedstrom1993cigs}.
A \gls{cigs} layer of 1-\um{2} thickness is applied on top via co-evaporation from elemental sources\cite{hedstrom1993cigs}.
The p-type doping of \gls{cigs} is achieved by adding more than stoichiometric copper to the mix. 
The heterojunction is then completed by deposition of \ch{CdS} n-type layer (typically \nm{50} thick).
\ch{CdS} was earlier used as front contact, but now only acts as n-type wide-gap window and buffer. 
%After the \ch{CdS} layer 
A window layer of intrinsic \ch{ZnO} is deposited after the \ch{CdS} layer, followed by a highly conductive aluminium doped layer. 
\ch{ZnO} has a band gap of \ev{3.2} and is therefore transparent for visible light. 
The \ch{ZnO} window layer (usually of thickness 50-\nm{70} is highly conductive (especially the aluminium doped layer) and acts as front contact.

%
Instead of glass as substrate, steel and polymers (e.g.\ polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Polymers generally have low thermal stability compared with ceramics and metals, which restrict the fabrication temperature of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
Thus, an insulating layer has to be deposited on the steel substrate. 
%The conductance of steel can be masked by a insulator layer (e.g.\ \ch{ZrO2}, \ch{Al2O3}).

@@

%\section{Materials and Their Analysis}
\section{Sample Preparation}
%\todo{COATING OF THE SUBSTRATE or sample preparation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties of Zirconium Oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV\cite{Anwar2017} and relative permittivity of circa 20 at room temperature\cite{kukli2001dielectric}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}). 
This prevents mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
\ch{ZrO2} is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and bases\cite{Nielsen2005}.
%Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contact Deposition by Sputtering}
%SPUTTERING FREEWRITING: 
% what is sputtering?
Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
% what can it be used for? 
%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
%
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputter-deposited thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.
% how does it work? 
%A plasma is created and the ions are accelerated to the surface. 
The ions which are accelerated to the surface originate mostly from a plasma.
The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
The cascade can reach the surface again. 
If the energy of an atom is larger than the binding energy, the atom is ejected. 
%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
a minimum pressure is needed to sustain the plasma.
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
% what is used? 
Nobel gases (e.g.\ argon) in plasma phase are mainly used for bombardment because of their inert properties. 
Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
%Reactive gases can be added (e.g.\ \ch{O2} or \ch{N2}).
In order to use sputtering for depositing a target material on top of a substrate material, 
the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).

@@

\iffalse
%\td{how does it work?}\\
A high voltage is applied to 
two parallel electrodes with low pressure gas in between. 
The target acts as as feedstock anode and the substrate (holder) as cathode (see figure \ref{fig:sputter0}).
%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
The anode, then, emits electrons, which collide with gas particles (mostly argon because of its inert nature and potential to transfer more kinetic than lighter noble gases). 
Some gas particles may get ionized by the collision and the gas cations are accelerated to the anode. 
If a cation has enough energy, it will bump off one or more atoms or molecules from the surface. 
This happens by a cascade of momentum transfers, which can reach the surface again (see figure \ref{fig:sputter1}). 
\fi

@@

\subsubsection{Infrared Spectroscopy}
% IR
\Gls{ir} light interacts with molecular vibrations, which is only a part of the degrees of freedom of a molecule.
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore be calculated to be
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active, except Raman spectroscopy. 
%\td(does Raman not also use IR)}
The absorption of \Gls{nir} electromagnetic waves involves excitations of non-fundamental vibrations, overtones and combination modes which lead to intricate patterns in the so called fingerprint region. 
These transition are mostly "forbidden" and allow analysis of bulk matter without extensive preparation
due to the deep penetration depth of \gls{nir} light\cite{bec2019breakthrough}.
\fi
%\td{describe simple IR with monochromator}

@@

\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident angle) were recorded with a Bruker Vertex 70 spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588} {\nano\meter}) and a silicon detector for visual and \gls{nir} light (\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). 
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
For transmittance the light entered the sample from the side with the coating layer. 
The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged in Opus software. % included in the spectrometer. 
%
%When the refractive index of two layers differ, light can be used to measure the thickness\cite{Dumin1967} of the optical less dense material.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-Ray Diffraction}
%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\gls{xrd} is used to study the crystalline structure of materials.
Since X-rays wavelengths (\num{0.2} to \nm{10}) are comparable to the interatomic spacing of crystalline solids, 
the beams get reflected and contain information about the structure\cite{Kaliva2020}.
Each crystalline material has a discreet atomic structure which upon irradiation with 
X-rays causes constructive and destructive interference according to Bragg's law and generates unique diffraction patterns. 
\Gls{xrd} diffraction plots of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad curve with a maximum extending over several degrees (2$\theta$).
